\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 evaluation.tex
update in the evaluation

After we fixed all the bugs we could find in the programs under test, we added options to the code to introduce various benchmark bugs (some that were actually in the original programs and some we made up) one at a time so we could evaluate different methods to detect and diagnose them.  We compare \psharp systematic concurrency testing to traditional ``stress testing'' without systematic concurrency control; we report the average length of time it took for the test to fail and remark on the effort needed to diagnose the bug from the test output. \MMComment{Overview of actual results?}

\subsection{Experimental Setup}

@@

Cheng's case study with the actual bug

After fixing all the bugs we found in MigratingTable, we added an option to conditionally reintroduce each of the following bugs:
\begin{enumerate}
\item Filtering on a user-defined property did not retrieve non-matching rows from the new table that might shadow a matching row from the old table.
\item ...
\end{enumerate}

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\label{tab:stats}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics.}
%\vspace{-3mm}
\end{table}

\subsection{Systematic testing with \psharp}

@@

How long you had to run the test to find the bug (if you can find it) and how long are the traces

How easy it is to pinpoint the error using the \psharp traces, comparing to traditional stress testing

Effort required to use the system

>>>>

We report our experience of applying \psharp on the three case studies discussed in this paper: Azure Storage vNext, Live Migration Table and Azure Service Fabric. We first discuss how much human effort was spent in modeling the environment of these case studies so they become amenable to testing with \psharp. We then present runtime results of using \psharp with two different systematic testing schedulers to find bugs in the case studies.

\subsection{Cost of modeling}

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\label{tab:stats}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from environmental modeling in the three case studies.}
%\vspace{-3mm}
\end{table}

\subsection{Cost of systematic testing}

After we fixed all the bugs we could find in the programs under test, we added options to the code to introduce various benchmark bugs (some that were actually in the original programs and some we made up) one at a time so we could evaluate different methods to detect and diagnose them.

After fixing all the bugs we found in MigratingTable, we added an option to conditionally reintroduce each of the following bugs.

@@

@@
